% Time-optimized global alignment algorithm (not yielding the optimal solution)

We aim to modify the aligment dynamic programming algorithm such that it does not guarantee an optimal solution, but have better time and space performance. We assume the two strings to be matched have length $n$. Let $t$ the value of a threshold.

If the edit distance (i.e. distance to the diagonal path in the edit matrix) exceeds $t$ in any direction, we stop considering the solution. In order to integrate this behavior in the existing DP algorithm, we propose the following modifications.

\textbf{Cost function}: We modify the cost evaluation to:
\[
  DP[i][j] = \left \{
    \begin{array}{ll}
      \infty & \text{if } |i - j| > t \\
      \text{Previous cost definition} & \text{otherwise} \\
    \end{array}
  \right.
\]

Then we notice that we only need to evaluate cells $(i, j)$ such that $|i - j| > t$. There are at most $2t$ such cells per line.

We use the same divide-and-conquer algorithm together with the standard dynamic programming algorithm $A$(as denoted in lecture notes). But instead of filling all $n$ entries on a row, the algorithm $A$ only fills in $2t$ entries per row.

As now we only care $2t$ entries per row, and algorithm $A$ only requires storage of three rows, so the storage requirement now is $O(t)$.

Now let's see what's the time performance:

\begin{itemize}
\item Running algorithm $A$ on the whole matrix to find optimal solution OPT takes $O(tn)$
\item Running algorithm $A$ on the first $n/2$ rows and last $n/2$ rows(backward) takes $O(tn)$.
\item Finding the $j$ on row $n/2$ such that $R_1[j] + R_2[j] = OPT$ takes $O(t)$.
\end{itemize}

So in total it takes $O(tn)$ to divide the problem to two subproblems. We have following recurrence relation:

\[
t(m,n) = t(j, n/2) + t(m−j,n/2) + \Theta(tn)
\]

Solving the equation above gives us $O(tn)$. So if $t$ is a constant, the memory usage is also constant and the time performance is linear.
