% Construct a path which minimizes the delay

We start with the following important observation:

\begin{quote}
  \textit{No matter from which point we start the path, the last visited point must be either to the very first or the very last of the line.}
\end{quote}

We number the points $p_i$ from left to right on the line, such that $p_1$ is the leftmost and $p_n$ is the rightmost point. Let's denote the last visited point as $p_k$ and the start point as $p_s$.

Suppose the observation doesn't hold. Then $p_k$ lies either in the interval $(p_1, p_s)$ or $(p_s, p_n)$. Because $p_k$ lies within the two intervals, it's impossible to visit $p_1$ and $p_n$ without visiting $p_k$. Thus $p_k$ can't be the last visited point.\\

Let us now consider the \textit{last visited consecutive sequence}. Last visited consecutive sequence is an array of points $A[1..k]$, where:

\begin{enumerate}
\item $A[i]$ and $A[i+1]$ are neighbors on the line
\item $A[i]$ is visited exactly before $A[i+1]$
\item $A[k]$ is the last visited point
\end{enumerate}

According to the observation above, the last visited consecutive consequence is either like $p_k, p_{k-1}, .., p_1$ or like $p_{k+1}, .., p_n$. Suppose the last visited consecutive sequence ends to the left. Let's visualize what it looks like:\\

% Define style for nodes
\tikzstyle{every node}=[circle, draw, fill=black!50,
                        inner sep=0pt, minimum width=4pt]
\begin{tikzpicture}[thick]
  \path[draw] (0, 0) -- (13, 0);

  \draw (1, 0) node[label=below:$p_1$] {};
  \draw (2.3,0) node[label=below:$p_2$] {};
  \draw (3, 0) node {};
  \draw (4.3,0) node {};
  \draw (4.7,0) node[label=below:$p_k$] {};

  \draw (5.8, 0) node[label={[label distance=0.3]below:$p_{k+1}$}] {};
  \draw (7.2, 0) node {};
  \draw (8, 0) node {};
  \draw (9.3, 0) node {};
  \draw (10.1, 0) node {};
  \draw (11.5, 0) node[label={[label distance=0.5]below:$p_n$}] {};

  \path[draw, dashed] (5, 0.2)-- (5, -0.2) -- (12, -0.2) -- (12, 0.2) -- cycle;

  \draw[->, |->] (11.5, 0.7) -- (1, 0.7);

\end{tikzpicture}\quad

In the graph above, $p_k, .., p_2, p_1$ is the last visited consecutive sequence. Then what can we say about the most recently visited point in the subpath $p_{k+1}, .., p_n$? Based on the previous observation, we know that either $p_{k+1}$ or $p_n$ must be the last visited point. However, if $p_{k+1}$ is the last visited point, we can grow our last visited consecutive sequence $p_k, .., p_2, p_1$ by $p_{k+1}$. Thus, we can conclude:

\begin{quote}
\textit{If $p_k, .., p_2, p_1$ is the last visited consecutive sequence, then the last visited point in $p_{k+1}, .., p_n$ is $p_n$.}
\end{quote}

With the property above, if we are given the optimal solution to the subproblem $p_{k+1}, .., p_n$, then a possible solution to the overall problem can be constructed by adding the delay of each point in the last visited consecutive sequence. As we know the last visited point in the subproblem is $p_n$, so for each point $p_i$ in the last visited consecutive sequence, its delay is $delay(p_n) + dist(p_i, p_n)$.

Similar arguments hold as well if the \textit{last visited consecutive consequence} is at the end of the array. Then we can decompose the problem into subproblems using following recurrence relation:

\[
OPT(p_1, p_2, .., p_n) = \min_{k \in [1..n]} \left\{
  \begin{array}{ll}
    OPT(p_{k+1}, .., p_n) + \sum_{i=1}^{k}(delay(p_n) + dist(p_i, p_n)) & Case 1 \\
    OPT(p_1, p_2, .., p_k) + \sum_{i=k+1}^{n}(delay(p_1) + dist(p_i, p_1)) & Case 2 \\
  \end{array}\right.
\]

In \textit{Case 1}, the last visited consecutive sequence is at the head of the array. In \textit{Case 2}, the last visited consecutive sequence is at the end of the array.

Given the recurrence relation above, the algorithm is straightforward. It computes the optimal solutions to all possible intervals $p_i, .., p_j$, starting from the base cases with a single element $p_i$ and finishing at $p_1, .., p_n$.\\

Now let's see the performance of the algorithm. There are exactly $n - k + 1$ intervals with size $k$. For each interval of size $k$, it has to select one optimal solution among the $2(k-1)$ possible divisions of subprolems. For each division of subproblems, it seems we need $k$ steps to compute the term $\sum_{i=1}^{k}(delay(p_n) + dist(p_i, p_n))$. However, notice that $dist(p_i, p_n) = dist(p_1, p_n) - dist(p_1, p_i)$, so we have the following:
\[
\sum_{i=1}^{k}(delay(p_n) + dist(p_i, p_n)) = k \cdot delay(p_n) + k \cdot dist(p_1, p_n) - \sum_{i=1}^{k}dist(p_1, p_i)
\]

In the equation above, both $k \cdot delay(p_n)$ and $k \cdot dist(p_1, p_n)$ can be computed in constant time. Using a memoization technique, it's easy to compute $\sum_{i=j}^{k}dist(p_j, p_i)$ for any interval $(p_j, p_k)$ in constant time, and the total cost is bounded by $O(n^2)$. So the summation term can be computed in constant time, and let's denote the constant as $c$. Thus the total cost is in:
\[
  O(n^2) + \sum_{i=1}^{n} (n - k + 1) \cdot 2(k - 1) \cdot c = O(n^3)
\]
