% Devise an MST algorithm for a particular family of graphs

We focus on the family of graphs which have a subset of $k$ edges whose removal turns the graph into a tree. Let $G = (E, V)$ a graph of this family and $E' \subseteq E$ the subset of edges of size $|E'| = k$. These $k$ edges must be part of at most $k$ cycles. We propose the following algorithm to remove these cycles and optain an MST in linear time:

\begin{enumerate}
  \item Start at any vertex $v$.
  \item Explore the graph in a depth-first fashion, maintaining a doubly-linked list of the current path.
  \begin{itemize}
    \item When a new node $v$ is encountered through an edge $e$: mark $v$ as visited, add $v$ to the current path list and add $e$ to the MST.
    \item When a previously visited node $u$ is encountered from $v$ through an edge $e$, then $e$ must be part of a cycle. The cycle starts at $u$, which must be part of the current path. Removing any edge from this path will break the cycle. We use our doubly-linked list to find the heaviest edge and remove it from the solution.
    \item When backtracking, remove nodes from the current path.
  \end{itemize}
  \item After all nodes have been marked, we obtain a Minimum Spanning Tree.
\end{enumerate}

\noindent
Since each node and edge are used exactly once, traversing the graph takes time $O(|V| + |E|)$. When searching for an edge to remove in order to break a cycle, we traverse the current path's list, of length at most $|V|$. There are $k$ such cycles, therefore our algorithm has a running time in $0(|V| + |E| + k \cdot |V|) = O(|V| + |E|)$.
